---
title: "Groundfish DST Summary"
output:
  html_document:
    theme: default
---
<style>
.main-container { width: 1500px; max-width:2800px;}
</style>
---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(scales)

options(scipen=999, 
        digits = 2) 


cod_acl <- function(){
    cod_acl = 118
    return(cod_acl)
  }

had_acl <- function(){
    had_acl = 1146
    return(had_acl)
  }

lb_to_mt <- function(){
    lb_to_mt = 0.000454
    return(lb_to_mt)
  }


fnames <- list.files(path=here::here("output/"),pattern = "*.csv",full.names = T)

fnames2<- as.data.frame(fnames) %>% 
  tidyr::separate(fnames, into = c("a", "b", "c"), sep = "_") %>% 
  dplyr::mutate(run_name = b) %>% 
  dplyr::select(run_name)

df <- fnames %>% 
  map_df(~data.table::fread(.,stringsAsFactors=F,check.names=T,strip.white=T))



######################## Compute scaled Mortality by Scaling Wave 5 removals weight ###################
# Read in Monthly results
month_file_names <- list.files(path=here::here("output/"),pattern = ".Rds",full.names = T)

adjusted_removals <- month_file_names %>% 
  map_df(~readRDS(.))

# Keep just removals, for both species
adjusted_removals<-adjusted_removals %>%
   dplyr::filter(metric == "removals_weight")

# Append scaling_factor
cod_W5scaling_factor<-3.65
haddock_W5scaling_factor<-0.45

adjusted_removals<-adjusted_removals %>%
   mutate(scaling_factor=case_when(
     species == "cod" & month %in% c(9,10) ~cod_W5scaling_factor,
     species == "hadd" & month %in% c(9,10) ~haddock_W5scaling_factor,
     .default=1)
  )

# Adjust removals weight by the scaling factor, and convert to metric_tons
adjusted_removals<-adjusted_removals %>%
      dplyr::mutate(value = value * scaling_factor* lb_to_mt())

# Contract to Annual
adjusted_removals<-adjusted_removals %>%
      dplyr::group_by(model, mode, species, draw) %>%
      dplyr::summarise(value = sum(value)) %>%
      dplyr::rename(adjusted_mortality_mt=value)

# check the number of times the policy is under the ACL, compute median adjusted removals 

adjusted_removals<-adjusted_removals %>%
      dplyr::mutate(under_acl = dplyr::case_when(species == "cod" & adjusted_mortality_mt <= cod_acl() ~ 1, TRUE ~ 0),
                    under_acl = dplyr::case_when(species == "hadd" & adjusted_mortality_mt <= had_acl() ~ 1, TRUE ~ under_acl)) %>%
      dplyr::group_by(mode, model, species) %>%
      dplyr::summarise(under_acl = sum(under_acl),
                       adjusted_mortality_mt = round(median(adjusted_mortality_mt),0)) %>%
      tidyr::pivot_wider(names_from = species, values_from = c(adjusted_mortality_mt, under_acl)) %>% 
  dplyr::mutate(model = gsub(" ", "", model))





```

## Total Mortality

```{r, out.width="100%"}
     catch_agg<- df %>%
      #dat %>%
      dplyr::filter(metric  == c("removals_weight"),
                    mode == "all modes")%>%
      dplyr::group_by(model, species,draw) %>%
      dplyr::summarise(Value = sum(as.numeric(value))) %>%
      dplyr::mutate(Value = Value * lb_to_mt()) %>%
      dplyr::mutate(under_acl = dplyr::case_when(species == "cod" & Value <= cod_acl() ~ 1, TRUE ~ 0),
                    under_acl = dplyr::case_when(species == "had" & Value <= had_acl() ~ 1, TRUE ~ under_acl)) %>%
      dplyr::group_by(model, species) %>%
      dplyr::summarise(under_acl = sum(under_acl),
                       Value = round(median(Value),0)) %>%
      tidyr::pivot_wider(names_from = species, values_from = c(Value, under_acl))

    catch_agg2<- catch_agg %>%
      dplyr::mutate(under_acl_cod2 = dplyr::case_when(under_acl_cod < 50 ~ "Less than 50%", TRUE ~ ""),
                    under_acl_cod2 = dplyr::case_when(under_acl_cod >= 50 & under_acl_cod < 60 ~ "50-59%", TRUE ~ under_acl_cod2),
                    under_acl_cod2 = dplyr::case_when(under_acl_cod >= 60 & under_acl_cod < 70~ "60-69%", TRUE ~ under_acl_cod2),
                    under_acl_cod2 = dplyr::case_when(under_acl_cod >= 70 & under_acl_cod < 80 ~ "70-79%", TRUE ~ under_acl_cod2),
                    under_acl_cod2 = dplyr::case_when(under_acl_cod >= 80 & under_acl_cod < 90 ~ "80-89%", TRUE ~ under_acl_cod2),
                    under_acl_cod2 = dplyr::case_when(under_acl_cod >= 90 & under_acl_cod <=100 ~ "90-100%", TRUE ~ under_acl_cod2)) %>%
      dplyr::mutate(under_acl_had2 = dplyr::case_when(under_acl_hadd < 50 ~ "Less than 50%", TRUE ~ ""),
                    under_acl_had2 = dplyr::case_when(under_acl_hadd >= 50 & under_acl_hadd < 60 ~ "50-59%", TRUE ~ under_acl_had2),
                    under_acl_had2 = dplyr::case_when(under_acl_hadd >= 60 & under_acl_hadd < 70~ "60-69%", TRUE ~ under_acl_had2),
                    under_acl_had2 = dplyr::case_when(under_acl_hadd >= 70 & under_acl_hadd < 80 ~ "70-79%", TRUE ~ under_acl_had2),
                    under_acl_had2 = dplyr::case_when(under_acl_hadd >= 80 & under_acl_hadd < 90 ~ "80-89%", TRUE ~ under_acl_had2),
                    under_acl_had2 = dplyr::case_when(under_acl_hadd >= 90 & under_acl_hadd <=100 ~ "90-100%", TRUE ~ under_acl_had2)) %>%
      dplyr::rename(`Cod Mortality`=Value_cod) %>%
      dplyr::rename(`Haddock Mortality`=Value_hadd) %>%
      dplyr::ungroup()

    p<- catch_agg2 %>%
      ggplot2::ggplot(ggplot2::aes(x = `Cod Mortality`, y = `Haddock Mortality`))+
      ggplot2::geom_point(ggplot2::aes(colour = under_acl_cod2, size = under_acl_had2)) +
      ggplot2::scale_color_manual(values = c("50-59%" = "#A9DFBF", "60-69%" = "#7DCEA0",
                                             "70-79%" = "#52BE80","80-89%" = "#27AE60",
                                             "90-100%" = "#1B5E20", "Less than 50%" = "red3"))+
      ggplot2::scale_size_manual(values = c("50-59%" = 1, "60-69%" = 1,
                                            "70-79%" = 1,"80-89%" = 1,
                                            "90-100%" = 1, "Less than 50%" = 1))+
      ggplot2::labs(colour="% of simulations under cod ACL",
                    size="% of simulations under haddock ACL")+
      ggplot2::geom_text(ggplot2::aes(label = model), check_overlap = TRUE)+
      ggplot2::geom_vline( xintercept =cod_acl(), linetype="dashed")+
      ggplot2::geom_hline( yintercept =had_acl(), color="grey45")+
      ggplot2::annotate(geom="text", x=cod_acl(), label="Cod ACL", y=1200) +
      ggplot2::annotate(geom="text", y=had_acl(), label="Had ACL", x=100) +
      ggplot2::guides(size = "none")+
      ggplot2::ggtitle("Cod and Haddock Mortality")+
      ggplot2::ylab("Median Recreational Haddock Mortality (mt)")+
      ggplot2::xlab("Median Recreational Cod Mortality (mt)")

    fig<- plotly::ggplotly(p) %>% #,
      plotly::style(textposition = "top center")
    fig


```



## Total recreational fishing mortaltiy

```{r, out.width="100%"}
dat<- df %>%
      dplyr::filter(metric == c("removals_weight"), 
                    species == "cod", 
                    mode == "all modes") %>%
      dplyr::group_by(model, species,draw) %>%
      dplyr::mutate(value = value * lb_to_mt()) %>% 
  dplyr::mutate(under_acl = dplyr::case_when(species == "cod" & value <= cod_acl() ~ 1, TRUE ~ 0))


p2<- dat %>% 
  ggplot(aes(x = model, y = value))+
  geom_point(color = "gray", alpha = 0.3, size = 2)+
  stat_summary( fun = median,geom = "point",color = "black",size = 3)+  # Median point
  ylab("Metric tons")+
  xlab(element_blank())+
  ggtitle("Cod total mortality")+
  theme_minimal() +
  geom_hline(aes(yintercept = cod_acl()), linetype = "dashed",
              color = "red", size = 1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
  



fig2<- plotly::ggplotly(p2) 
fig2
  
```


```{r, out.width="100%"}
dat<- df %>%
      dplyr::filter(metric %in% c("removals_weight"), species == "hadd", 
                    mode == "all modes") %>%
      dplyr::group_by(model, species,draw) %>%
      dplyr::mutate(value = value * lb_to_mt()) %>% 
  dplyr::mutate(under_acl = dplyr::case_when(species == "cod" & value <= had_acl() ~ 1, TRUE ~ 0))

p2<- dat %>% 
  ggplot(aes(x = model, y = value))+
  geom_point(color = "gray", alpha = 0.3, size = 2)+
  stat_summary( fun = median,geom = "point",color = "black",size = 3)+  # Median point
  ylab("Metric tons")+
  xlab(element_blank())+
  ggtitle("Haddock total mortality")+
  theme_minimal() +
  geom_hline(aes(yintercept = had_acl()), linetype = "dashed",
              color = "red", size = 1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

fig2<- plotly::ggplotly(p2) 
fig2
```


### Angler satisfaction (consumer surplus, $)
How much better off will anglers be next year compared to last year, in dollars?

```{r, out.width="100%"}

cv_agg<- df %>%
  dplyr::filter(metric == c("CV"), 
                mode == "all modes") %>%
  dplyr::mutate(value=(value)/1000000)

cv_plot<-cv_agg %>% 
  ggplot( aes(x = model, y = value)) +
  geom_point(alpha = .4,  size = 2, color = "gray")+ 
  #scale_color_manual(values=c("#56B4E9", "blue", "grey"))+ # Jittered points
  stat_summary( fun = median,geom = "point",color = "black",size = 3)+  # Median point
  labs(
    title = "",
    x = "",
    y = "million $"
  ) +
  theme_minimal() +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

fig3<- plotly::ggplotly(cv_plot) %>% 
      plotly::style(textposition = "top center")

fig3
  
```

### Dead discards

```{r, out.width="100%"}
dat<- df %>%
      dplyr::filter(metric == "discmort_weight", 
                    species == "cod", 
                    mode == "all modes") %>%
      dplyr::group_by(model, species,draw) %>%
      dplyr::summarise(value = sum(as.numeric(value))) %>%
      dplyr::mutate(value = value * lb_to_mt())

# dat2$Label <- paste0("% runs < ACL: ", round(dat2$under_acl, .01))
# dat2$Label <- paste0("% runs < ACL: ", round(dat2$under_acl, .01))
ylim_l<-min(dat$Value-5)
ylim_u<-max(dat$Value+5)

# dat2$run_number <- factor(dat2$run_number, levels = ordered_groups)
# dat$run_number <- factor(dat$run_number, levels = ordered_groups)

p2<-dat %>% 
  ggplot(aes(x = model, y = value))+
  geom_point(alpha = .4,  size = 2, color = "gray") + 
  #scale_color_manual(values=c("#56B4E9", "blue", "grey"))+  # Jittered points
  stat_summary( fun = median,geom = "point",color = "black",size = 3)+  # Median point
  # geom_errorbar(data = dat2, aes(x = run_number, ymin = ci_lower, ymax = ci_upper),
  #               inherit.aes = FALSE, width = 0.1, color = "black")+
  ylab("Metric tons")+
  xlab(element_blank())+
  ggtitle("Cod discard mortality")+
    theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) #+
  #geom_text(data = dat2,
  #          aes(x = run_number, y = min(dat$Value) - 5, label = Label),  
  #          inherit.aes = FALSE, hjust = 0.5, vjust = 1, size = 3.5,color = "black") +
  # ylim(ylim_l, ylim_u)  + 
  # scale_y_continuous(breaks = seq(round(ylim_l, -1), round(ylim_u,-1), by = 10))+
  #   theme(legend.position="none")
  

fig2<- plotly::ggplotly(p2) 
fig2
  
```

```{r, out.width="100%"}

dat<- df %>%
      dplyr::filter(metric == "discmort_weight", 
                    species == "hadd", 
                    mode == "all modes") %>%
      dplyr::group_by(model, species,draw) %>%
      dplyr::summarise(value = sum(as.numeric(value))) %>%
      dplyr::mutate(value = value * lb_to_mt())

# dat2$Label <- paste0("% runs < ACL: ", round(dat2$under_acl, .01))
# dat2$Label <- paste0("% runs < ACL: ", round(dat2$under_acl, .01))
# ylim_l<-min(dat$Value-5)
# ylim_u<-max(dat$Value+5)

# dat2$run_number <- factor(dat2$run_number, levels = ordered_groups)
# dat$run_number <- factor(dat$run_number, levels = ordered_groups)

p2<-dat %>% 
  ggplot(aes(x = model, y = value))+
  geom_point(alpha = .4,  size = 2, color = "gray") + 
  #scale_color_manual(values=c("#56B4E9", "blue", "grey"))+  # Jittered points
  stat_summary( fun = median,geom = "point",color = "black",size = 3)+  # Median point
  # geom_errorbar(data = dat2, aes(x = run_number, ymin = ci_lower, ymax = ci_upper),
  #               inherit.aes = FALSE, width = 0.1, color = "black")+
  ylab("Metric tons")+
  xlab(element_blank())+
  ggtitle("Haddock discard mortality")+
    theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  #+
  #geom_text(data = dat2,
  #          aes(x = run_number, y = min(dat$Value) - 5, label = Label),  
  #          inherit.aes = FALSE, hjust = 0.5, vjust = 1, size = 3.5,color = "black") +
  # ylim(ylim_l, ylim_u)  + 
  # scale_y_continuous(breaks = seq(round(ylim_l, -1), round(ylim_u,-1), by = 10))+
  #   theme(legend.position="none")
  

fig2<- plotly::ggplotly(p2) 
fig2
```


## Individual Policy Results {.tabset}
```{r}
## Regulations
regulations <- function(model){
     regs <- readr::read_csv(here::here(paste0("saved_regs/regs_", model,".csv")))


    regs1 <- regs %>%
      dplyr::rename("model" = "run_name") %>%
      #dplyr::left_join(catch_agg, by = c("model")) %>%
      dplyr::mutate(
        species = stringr::str_extract(input, "^[a-z]+"),
        mode    = stringr::str_extract(input, "(FH|PR)"),
        season  = stringr::str_extract(input, "\\d+"),
        bound   = stringr::str_extract(input, "(op|cl)"),
        value    = stringr::str_remove(value, "^\\d{4}-")  # remove year
      ) %>%
      dplyr::group_by(model, species, mode, season) %>%
      dplyr::filter(!any(value == 0))

    seasons <- regs1 %>%
      dplyr::select(!input) %>%
      dplyr::filter(bound %in% c("op", "cl")) %>%
      tidyr::pivot_wider(names_from = bound,values_from = value) %>%
      dplyr::mutate(season_range = paste(op, "-", cl)) %>%
      dplyr::group_by(model, species, mode) %>%
      dplyr::summarise(season = paste(season_range, collapse = " ; "),.groups = "drop") %>%
      tidyr::pivot_wider(names_from = species, values_from = season, names_glue = "{species}season")


    bags <- regs1 %>%
      dplyr::filter(stringr::str_detect(input, "bag")) %>%
      dplyr::mutate(bag_type = paste0(species, "bag")) %>%
      dplyr::group_by(model, mode, bag_type) %>%
      dplyr::summarise(bag = dplyr::first(value), .groups = "drop") %>%
      tidyr::pivot_wider(names_from = bag_type,values_from = bag)

    minsizes <- regs1 %>%
      dplyr::filter(stringr::str_detect(input, "len")) %>%
      dplyr::mutate(size_type = paste0(species, "len")) %>%
      dplyr::group_by(model, mode, size_type) %>%
      dplyr::summarise(size = dplyr::first(value), .groups = "drop") %>%
      tidyr::pivot_wider(names_from = size_type,values_from = size)

    final_table <- seasons %>%
      dplyr::left_join(bags, by = c("model", "mode")) %>%
      dplyr::left_join(minsizes, by = c("model", "mode")) %>%
      dplyr::mutate(codseason = if (!"codseason" %in% names(.)) NA_character_ else codseason, 
                    codbag = if (!"codbag" %in% names(.)) NA_character_ else codbag, 
                    codlen = if (!"codlen" %in% names(.)) NA_character_ else codlen) %>% 
      #dplyr::left_join(catch_agg, by = c("model")) %>%
      dplyr::select(model, mode, codseason, codbag, codlen, hadseason, hadbag, hadlen) %>%
      dplyr::rename(Mode = mode,
                    `Policy Identifier` = model,
                    `Cod Bag Limit` = codbag,
                    `Cod Minimum Size (in)` = codlen,
                    `Cod Season(s)` = codseason,
                    `Haddock Bag Limit` = hadbag,
                    `Haddock Minimum Size (in)` = hadlen,
                    `Haddock Season(s)` = hadseason)


    knitr::kable(final_table)
}

## Mortality
total_mortality<- function(select_model){

 file <- list.files(path = here::here("output"), pattern = paste0("^output_", select_model, "_.*\\.csv$"),,full.names = TRUE ) |>
    tibble(file = _) |>
    mutate(mtime = file.info(file)$mtime) |>
    arrange(desc(mtime)) |>
    slice(1) |>
    pull(file)
  
  mort <- read_csv(file)  %>%
      dplyr::filter(metric == c("removals_weight"),
                    mode == "all modes")%>%
      dplyr::group_by(model, species,draw) %>%
      dplyr::summarise(Value = sum(as.numeric(value))) %>%
      dplyr::mutate(Value = Value * lb_to_mt()) %>%
      dplyr::mutate(under_acl = dplyr::case_when(species == "cod" & Value <= cod_acl() ~ 1, TRUE ~ 0),
                    under_acl = dplyr::case_when(species == "hadd" & Value <= had_acl() ~ 1, TRUE ~ under_acl)) %>%
      dplyr::group_by(model, species) %>%
      dplyr::summarise(under_acl = sum(under_acl),
                       Value = round(median(Value),0)) %>%
    dplyr::mutate(across(where(is.numeric),~ comma(round(.x, 2)))) %>% 
      tidyr::pivot_wider(names_from = species, values_from = c(Value, under_acl)) %>% 
    dplyr::rename(`% under Cod ACL` = under_acl_cod,
                  `% under Haddock ACL` = under_acl_hadd,
                  `Cod Mortality (mt)` = Value_cod,
                  `Haddock Mortality (mt)` = Value_hadd)
  
  mort2<- adjusted_removals %>% dplyr::filter(model == select_model, 
                                              mode == "all modes") %>% 
    dplyr::ungroup() %>% 
    dplyr::select(-"mode", -"model") %>% 
    dplyr::rename(`% under Cod ACL - new MRIP data` = under_acl_cod,
                  `% under Haddock ACL - new MRIP data` = under_acl_hadd,
                  `Cod Mortality (mt) - new MRIP data` = adjusted_mortality_mt_cod ,
                  `Haddock Mortality (mt) - new MRIP data` = adjusted_mortality_mt_hadd )
  
  mort<- mort %>% cbind(mort2) %>% 
    dplyr::rename(`Policy Identifier` = model) 
  
  
  knitr::kable(mort)
}

total_mortality_mode<- function(model){
  file <- list.files(path = here::here("output"), pattern = paste0("^output_", model, "_.*\\.csv$"),,full.names = TRUE ) |>
    tibble(file = _) |>
    mutate(mtime = file.info(file)$mtime) |>
    arrange(desc(mtime)) |>
    slice(1) |>
    pull(file)
  
  mort_mode <- read_csv(file)  %>%
      dplyr::filter(metric == c("removals_weight"),
                    !mode == "all modes")%>%
      dplyr::group_by(model, species,draw, mode) %>%
      dplyr::summarise(Value = sum(as.numeric(value))) %>%
      dplyr::mutate(Value = Value * lb_to_mt()) %>%
      # dplyr::mutate(under_acl = dplyr::case_when(species == "cod" & Value <= cod_acl() ~ 1, TRUE ~ 0),
      #               under_acl = dplyr::case_when(species == "hadd" & Value <= had_acl() ~ 1, TRUE ~ under_acl)) %>%
      dplyr::group_by(model, species, mode) %>%
      dplyr::summarise(#under_acl = sum(under_acl),
                       Value = round(median(Value),0)) %>%
    dplyr::mutate(across(where(is.numeric),~ comma(round(.x, 2)))) %>% 
      tidyr::pivot_wider(names_from = species, values_from = c(Value)) %>% 
    dplyr::rename(`Policy Identifier` = model, 
                  `Cod Mortality (mt)` = cod,
                  `Haddock Mortality (mt)` = hadd)
  knitr::kable(mort_mode, digits = 2)
}

## Keep/Release/Dead Discards
keep_release<- function(model){
  file <- list.files(path = here::here("output"), pattern = paste0("^output_", model, "_.*\\.csv$"),,full.names = TRUE ) |>
    tibble(file = _) |>
    mutate(mtime = file.info(file)$mtime) |>
    arrange(desc(mtime)) |>
    slice(1) |>
    pull(file)
  
  keep_rel <-  read_csv(file)  %>%
    dplyr::filter(grepl("number|weight", metric)) %>% 
    dplyr::filter(mode == "all modes") %>% 
    dplyr::mutate(Variable = metric) %>%
    dplyr::group_by(species, Variable, model) %>%
    dplyr::summarise( total = median(value, na.rm = TRUE), .groups = "drop") %>%
    dplyr::mutate(total = ifelse(Variable %in% c("keep_weight", "release_weight", "discmort_weight","removals_weight"), 
                          total * lb_to_mt(), 
                          total)) %>%
    dplyr::mutate(across(where(is.numeric),~ comma(round(.x, 2)))) %>% 
    tidyr::pivot_wider(names_from = Variable, values_from = total) %>% 
    dplyr::select(model, species,keep_numbers,keep_weight, release_numbers,release_weight, 
                  discmort_number,discmort_weight, removals_number, removals_weight ) %>% 
    dplyr::rename(`Policy Identifier` = model, 
                  Species = species, 
                  `Harvest in Numbers` = keep_numbers,
                  `Harvest (mt)` = keep_weight,
                  `Discards in Numbers` = release_numbers,
                  `Discards (mt)` = release_weight,
                  `Dead Discards in Numbers` = discmort_number,
                  `Dead Discards (mt)` = discmort_weight,
                  `Total Mortality in Numbers` = removals_number,
                  `Total Mortality (mt)` = removals_weight)
  knitr::kable(keep_rel)
}

keep_release_mode<- function(model){
    file <- list.files(path = here::here("output"), pattern = paste0("^output_", model, "_.*\\.csv$"),,full.names = TRUE ) |>
    tibble(file = _) |>
    mutate(mtime = file.info(file)$mtime) |>
    arrange(desc(mtime)) |>
    slice(1) |>
    pull(file)
  
  keep_rel_mode <-  read_csv(file)  %>%
    dplyr::filter(grepl("number|weight", metric)) %>% 
    dplyr::filter(!mode == "all modes") %>% 
    mutate(Variable = metric) %>%
    group_by(species, Variable, model, mode) %>%
    summarise( total = median(value, na.rm = TRUE), .groups = "drop") %>%
    mutate(total = ifelse(Variable %in% c("keep_weight", "release_weight", "discmort_weight","removals_weight"), 
                          total * lb_to_mt(), 
                          total)) %>%
    dplyr::mutate(across(where(is.numeric),~ comma(round(.x, 2)))) %>% 
    tidyr::pivot_wider(names_from = Variable, values_from = total) %>% 
    dplyr::select(model, species, mode, keep_numbers,keep_weight, release_numbers,release_weight, 
                  discmort_number,discmort_weight, removals_number, removals_weight ) %>% 
    dplyr::rename(`Policy Identifier` = model, 
                  Species = species, 
                  `Harvest in Numbers` = keep_numbers,
                  `Harvest (mt)` = keep_weight,
                  `Discards in Numbers` = release_numbers,
                  `Discards (mt)` = release_weight,
                  `Dead Discards in Numbers` = discmort_number,
                  `Dead Discards (mt)` = discmort_weight,
                  `Total Mortality in Numbers` = removals_number,
                  `Total Mortality (mt)` = removals_weight)
  knitr::kable(keep_rel_mode)
}


## angler satisfaction and trips
cv_trips<- function(model){
    file <- list.files(path = here::here("output"), pattern = paste0("^output_", model, "_.*\\.csv$"),,full.names = TRUE ) |>
    tibble(file = _) |>
    mutate(mtime = file.info(file)$mtime) |>
    arrange(desc(mtime)) |>
    slice(1) |>
    pull(file)
  
  cv_trips <-  read_csv(file)  %>%
    dplyr::filter(metric %in% c("CV", "predicted_trips")) %>% 
    dplyr::filter(mode == "all modes") %>% 
    mutate(Variable = metric) %>%
    group_by(species, Variable, model) %>%
    summarise( total = median(value, na.rm = TRUE), .groups = "drop") %>% 
    dplyr::mutate(across(where(is.numeric),~ comma(round(.x, 2)))) %>% 
    tidyr::pivot_wider(names_from = Variable, values_from = total) %>% 
    dplyr::select(model, predicted_trips, CV) %>% 
    dplyr::rename(`Policy Identifier` = model, 
                  `Estimated number of trips` = predicted_trips, 
                  `Angler Satisfaction` = CV)
  knitr::kable(cv_trips)
}

cv_trips_mode<- function(model){
   file <- list.files(path = here::here("output"), pattern = paste0("^output_", model, "_.*\\.csv$"),,full.names = TRUE ) |>
    tibble(file = _) |>
    mutate(mtime = file.info(file)$mtime) |>
    arrange(desc(mtime)) |>
    slice(1) |>
    pull(file)
  
  cv_trips_mode <-  read_csv(file)  %>%
    dplyr::filter(metric %in% c("CV", "predicted_trips")) %>% 
    dplyr::filter(!mode == "all modes") %>% 
    mutate(Variable = metric) %>%
    group_by(species, Variable, model,mode ) %>%
    summarise( total = median(value, na.rm = TRUE), .groups = "drop") %>%
    dplyr::mutate(across(where(is.numeric),~ comma(round(.x, 2)))) %>% 
    tidyr::pivot_wider(names_from = Variable, values_from = total) %>% 
    dplyr::select(model, mode, predicted_trips, CV) %>% 
    dplyr::rename(`Policy Identifier` = model, 
                  `Estimated number of trips` = predicted_trips, 
                  `Angler Satisfaction` = CV)
  knitr::kable(cv_trips_mode)
}
```

### SQproposed {.tabset}

```{r}
regulations("SQproposed")
```

#### Total mortality

```{r}
total_mortality("SQproposed")

```

```{r}
total_mortality_mode("SQproposed")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("SQproposed")
```

```{r}
keep_release_mode("SQproposed")
```

#### Angler satisfaction/trips

```{r}
cv_trips("SQproposed")
```


```{r}

cv_trips_mode("SQproposed")
```


### SQactual {.tabset}

```{r}
regulations("SQactual")
```

#### Total mortality

```{r}
total_mortality("SQactual")

```

```{r}
total_mortality_mode("SQactual")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("SQactual")
```

```{r}
keep_release_mode("SQactual")
```

#### Angler satisfaction/trips

```{r}
cv_trips("SQactual")
```


```{r}

cv_trips_mode("SQactual")
```


### JS1 {.tabset}

```{r}
regulations("JS1")
```

#### Total mortality

```{r}
total_mortality("JS1")

```

```{r}
total_mortality_mode("JS1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("JS1")
```

```{r}
keep_release_mode("JS1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("JS1")
```


```{r}

cv_trips_mode("JS1")
```


### JS2 {.tabset}

```{r}
regulations("JS2")
```

#### Total mortality

```{r}
total_mortality("JS2")

```

```{r}
total_mortality_mode("JS2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("JS2")
```

```{r}
keep_release_mode("JS2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("JS2")
```


```{r}

cv_trips_mode("JS2")
```

### KLB2 {.tabset}

```{r}
regulations("KLB2")
```

#### Total mortality

```{r}
total_mortality("KLB2")

```

```{r}
total_mortality_mode("KLB2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("KLB2")
```

```{r}
keep_release_mode("KLB2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("KLB2")
```


```{r}

cv_trips_mode("KLB2")
```


### KLB7 {.tabset}

```{r}
regulations("KLB7")
```

#### Total mortality

```{r}
total_mortality("KLB7")

```

```{r}
total_mortality_mode("KLB7")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("KLB7")
```

```{r}
keep_release_mode("KLB7")
```

#### Angler satisfaction/trips

```{r}
cv_trips("KLB7")
```


```{r}

cv_trips_mode("KLB7")
```




### KLB8 {.tabset}

```{r}
regulations("KLB8")
```

#### Total mortality

```{r}
total_mortality("KLB8")

```

```{r}
total_mortality_mode("KLB8")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("KLB8")
```

```{r}
keep_release_mode("KLB8")
```

#### Angler satisfaction/trips

```{r}
cv_trips("KLB8")
```


```{r}

cv_trips_mode("KLB8")
```


### KLB9 {.tabset}

```{r}
regulations("KLB9")
```

#### Total mortality

```{r}
total_mortality("KLB9")

```

```{r}
total_mortality_mode("KLB9")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("KLB9")
```

```{r}
keep_release_mode("KLB9")
```

#### Angler satisfaction/trips

```{r}
cv_trips("KLB9")
```


```{r}

cv_trips_mode("KLB9")
```



### MHA1 {.tabset}

```{r}
regulations("MHA1")
```

#### Total mortality

```{r}
total_mortality("MHA1")

```

```{r}
total_mortality_mode("MHA1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MHA1")
```

```{r}
keep_release_mode("MHA1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MHA1")
```

```{r}
cv_trips_mode("MHA1")
```


### MHA2 {.tabset}

```{r}
regulations("MHA2")
```

#### Total mortality

```{r}
total_mortality("MHA2")

```

```{r}
total_mortality_mode("MHA2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MHA2")
```

```{r}
keep_release_mode("MHA2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MHA2")
```

```{r}
cv_trips_mode("MHA2")
```


### MJP {.tabset}

```{r}
regulations("MJP")
```

#### Total mortality

```{r}
total_mortality("MJP")

```

```{r}
total_mortality_mode("MJP")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MJP")
```

```{r}
keep_release_mode("MJP")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MJP")
```


```{r}

cv_trips_mode("MJP")
```



### MJP1 {.tabset}

```{r}
regulations("MJP1")
```

#### Total mortality

```{r}
total_mortality("MJP1")

```

```{r}
total_mortality_mode("MJP1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MJP1")
```

```{r}
keep_release_mode("MJP1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MJP1")
```


```{r}

cv_trips_mode("MJP1")
```




### MP C & H {.tabset}

```{r}
regulations("MPC&H")
```

#### Total mortality

```{r}
total_mortality("MPC&H")

```

```{r}
total_mortality_mode("MPC&H")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MPC&H")
```

```{r}
keep_release_mode("MPC&H")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MPC&H")
```

```{r}
cv_trips_mode("MPC&H")
```


### MP C & H 1 {.tabset}

```{r}
regulations("MPC&H1")
```

#### Total mortality

```{r}
total_mortality("MPC&H1")

```

```{r}
total_mortality_mode("MPC&H1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MPC&H1")
```

```{r}
keep_release_mode("MPC&H1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MPC&H1")
```


```{r}

cv_trips_mode("MPC&H1")
```


### MP FH S&F {.tabset}

```{r}
regulations("MPFHS&F")
```

#### Total mortality

```{r}
total_mortality("MPFHS&F")

```

```{r}
total_mortality_mode("MPFHS&F")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MPFHS&F")
```

```{r}
keep_release_mode("MPFHS&F")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MPFHS&F")
```

```{r}
cv_trips_mode("MPFHS&F")
```


### MP FH S&F1 {.tabset}

```{r}
regulations("MPFHS&F1")
```

#### Total mortality

```{r}
total_mortality("MPFHS&F1")

```

```{r}
total_mortality_mode("MPFHS&F1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MPFHS&F1")
```

```{r}
keep_release_mode("MPFHS&F1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MPFHS&F1")
```

```{r}
cv_trips_mode("MPFHS&F1")
```



### MP1 {.tabset}

```{r}
regulations("MP1")
```

#### Total mortality

```{r}
total_mortality("MP1")

```

```{r}
total_mortality_mode("MP1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MP1")
```

```{r}
keep_release_mode("MP1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MP1")
```


```{r}

cv_trips_mode("MP1")
```


### MP2 {.tabset}

```{r}
regulations("MP2")
```

#### Total mortality

```{r}
total_mortality("MP2")

```

```{r}
total_mortality_mode("MP2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MP2")
```

```{r}
keep_release_mode("MP2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MP2")
```


```{r}

cv_trips_mode("MP2")
```


### MP3 {.tabset}

```{r}
regulations("MP3")
```

#### Total mortality

```{r}
total_mortality("MP3")

```

```{r}
total_mortality_mode("MP3")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MP3")
```

```{r}
keep_release_mode("MP3")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MP3")
```

```{r}
cv_trips_mode("MP3")
```


### MP4 {.tabset}

```{r}
regulations("MP4")
```

#### Total mortality

```{r}
total_mortality("MP4")

```

```{r}
total_mortality_mode("MP4")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MP4")
```

```{r}
keep_release_mode("MP4")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MP4")
```

```{r}
cv_trips_mode("MP4")
```


### MP5 {.tabset}

```{r}
regulations("MP5")
```

#### Total mortality

```{r}
total_mortality("MP5")

```

```{r}
total_mortality_mode("MP5")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MP5")
```

```{r}
keep_release_mode("MP5")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MP5")
```


```{r}

cv_trips_mode("MP5")
```


### MPH {.tabset}

```{r}
regulations("MPH")
```

#### Total mortality

```{r}
total_mortality("MPH")

```

```{r}
total_mortality_mode("MPH")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MPH")
```

```{r}
keep_release_mode("MPH")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MPH")
```


```{r}

cv_trips_mode("MPH")
```


### MPH2 {.tabset}

```{r}
regulations("MPH2")
```

#### Total mortality

```{r}
total_mortality("MPH2")

```

```{r}
total_mortality_mode("MPH2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MPH2")
```

```{r}
keep_release_mode("MPH2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MPH2")
```

```{r}
cv_trips_mode("MPH2")
```


### MSG1 {.tabset}

```{r}
regulations("MSG1")
```

#### Total mortality

```{r}
total_mortality("MSG1")

```

```{r}
total_mortality_mode("MSG1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MSG1")
```

```{r}
keep_release_mode("MSG1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MSG1")
```


```{r}

cv_trips_mode("MSG1")
```



### MSG2 {.tabset}

```{r}
regulations("MSG2")
```

#### Total mortality

```{r}
total_mortality("MSG2")

```

```{r}
total_mortality_mode("MSG2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MSG2")
```

```{r}
keep_release_mode("MSG2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MSG2")
```


```{r}

cv_trips_mode("MSG2")
```










### MW1 {.tabset}

```{r}
regulations("MW1")
```

#### Total mortality

```{r}
total_mortality("MW1")

```

```{r}
total_mortality_mode("MW1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MW1")
```

```{r}
keep_release_mode("MW1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MW1")
```

```{r}
cv_trips_mode("MW1")
```



### MW2 {.tabset}

```{r}
regulations("MW2")
```

#### Total mortality

```{r}
total_mortality("MW2")

```

```{r}
total_mortality_mode("MW2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MW2")
```

```{r}
keep_release_mode("MW2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MW2")
```

```{r}
cv_trips_mode("MW2")
```


### MW3 {.tabset}

```{r}
regulations("MW3")
```

#### Total mortality

```{r}
total_mortality("MW3")

```

```{r}
total_mortality_mode("MW3")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("MW3")
```

```{r}
keep_release_mode("MW3")
```

#### Angler satisfaction/trips

```{r}
cv_trips("MW3")
```


```{r}

cv_trips_mode("MW3")
```


### WRTlll1  {.tabset}

```{r}
regulations("WRTlll1")
```

#### Total mortality

```{r}
total_mortality("WRTlll1")

```

```{r}
total_mortality_mode("WRTlll1")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("WRTlll1")
```

```{r}
keep_release_mode("WRTlll1")
```

#### Angler satisfaction/trips

```{r}
cv_trips("WRTlll1")
```


```{r}

cv_trips_mode("WRTlll1")
```


### WRTlll2 {.tabset}

```{r}
regulations("WRTlll2")
```

#### Total mortality

```{r}
total_mortality("WRTlll2")

```

```{r}
total_mortality_mode("WRTlll2")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("WRTlll2")
```

```{r}
keep_release_mode("WRTlll2")
```

#### Angler satisfaction/trips

```{r}
cv_trips("WRTlll2")
```

```{r}
cv_trips_mode("WRTlll2")
```


### WRTlll5 {.tabset}

```{r}
regulations("WRTlll5")
```

#### Total mortality

```{r}
total_mortality("WRTlll5")

```

```{r}
total_mortality_mode("WRTlll5")
```

#### Keep/Release/Dead Discards

```{r}
keep_release("WRTlll5")
```

```{r}
keep_release_mode("WRTlll5")
```

#### Angler satisfaction/trips

```{r}
cv_trips("WRTlll5")
```

```{r}
cv_trips_mode("WRTlll5")
```


