---
title: "Cod and Haddock Model Summary <br> `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

This page summarizes models results for sets of policies that have been run to date.  These are intended as a jumping off point for your own model runs.  


The results of your own model runs are stored. Please give it a name (please no underscores "_" ).  At the end of the day, they are added to this page.  

Hover over each point to view the detailed statistics for each model run.  The first section contains a table of recreational management measures. The second section contains graphs of mortality.   The third section has graphs of other performance measures, including Economic Surplus, Trips, and Discards. 

```{r setup, echo  = FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
library(grid)
library(plotly)

options(scipen=999) 

fnames <- list.files(path=here::here("output/"),pattern = "*.csv",full.names = T)

fnames2<- as.data.frame(fnames) %>% 
  tidyr::separate(fnames, into = c("a", "b", "c"), sep = "_") %>% 
  dplyr::mutate(c = ifelse(stringr::str_detect(c, "20241"),  "NA", c), 
                d = c(1:nrow(.)), 
                run_name = dplyr::case_when(c != "NA" ~ c, TRUE ~ as.character(d))) %>% 
  dplyr::select(run_name)

df <- fnames %>% 
  map_df(~data.table::fread(.,stringsAsFactors=F,check.names=T,strip.white=T))


df2<- df %>% dplyr::mutate(run_number = as.character(rep(fnames2$run_name, each = 90)))

cod_acl <- 99
had_acl <- 1075

lb_to_mt <-  0.000454 

```

# Management Measures

```{r,  echo  = FALSE, warning = FALSE, message = FALSE}


SQ_regulations <- read.csv(here::here("data-raw/SQ_regulations.csv")) %>% 
  dplyr::rename(Category = Var, 
                SQ = Val)



df3<- df2 %>% dplyr::filter(!Category %in% c("CV", "ntrips", "nchoiceoccasions","cod" , "had")) %>% 
  dplyr::select(Category, Value, run_number) %>% 
  dplyr::left_join(SQ_regulations, by = c("Category")) 



seas<- df3 %>% dplyr::filter(stringr::str_detect(Category, "Season")) %>% 
  tidyr::separate(Value, into = c("Value1", "Value2"), sep = " - ") %>% 
  tidyr::separate(SQ, into = c("SQ1", "SQ2"), sep = " - ") %>% 
  dplyr::mutate(Value = as.integer(lubridate::ymd(Value2)-lubridate::ymd(Value1)), 
                SQ = as.integer(lubridate::ymd(SQ2)-lubridate::ymd(SQ1))) %>% 
  dplyr::mutate(Diff_from_SQ = dplyr::case_when(Value < SQ ~ "Shorter_Season", TRUE ~ ""),
                Diff_from_SQ = dplyr::case_when(Value > SQ ~ "Longer_Season", TRUE ~ Diff_from_SQ), 
                Value = paste0(Value1, " - ", Value2)) %>% 
  dplyr::select(Category, Diff_from_SQ, run_number) 
                  
bag<- df3 %>% dplyr::filter(stringr::str_detect(Category, "bag")) %>% 
  dplyr::mutate(Diff_from_SQ = dplyr::case_when(as.numeric(Value) < as.numeric(SQ) ~ "Smaller Bag", TRUE ~ ""),
                Diff_from_SQ = dplyr::case_when(as.numeric(Value) > as.numeric(SQ) ~ "Larger Bag", TRUE ~ Diff_from_SQ)) %>% 
  dplyr::select(Category, Diff_from_SQ, run_number)

size<- df3 %>% dplyr::filter(stringr::str_detect(Category, "size")) %>% 
  dplyr::mutate(Diff_from_SQ = dplyr::case_when(as.numeric(Value) < as.numeric(SQ) ~ "Smaller Min Length", TRUE ~ ""),
                Diff_from_SQ = dplyr::case_when(as.numeric(Value) > as.numeric(SQ) ~ "Larger Min Length", TRUE ~ Diff_from_SQ)) %>% 
  dplyr::select(Category, Diff_from_SQ, run_number)

df4<- rbind(seas, bag, size) %>% 
  dplyr::ungroup()

Regs_out <- df3 %>%
  dplyr::left_join(df4, by = c("Category", "run_number")) %>% 
  dplyr::select(!SQ) %>% 
  dplyr::select(!Opt) %>% 
  tidyr::separate(Category, into =c("Species", "mode", "Var"), sep = "_") %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_wider(names_from = Var, values_from = c(Value, Diff_from_SQ)) %>%
  dplyr::mutate(Value_Season = dplyr::case_when(Value_bag == 0 ~"NA", TRUE ~ Value_Season), 
                Value_size = dplyr::case_when(Value_bag == 0 ~"NA", TRUE ~ Value_size), 
                Diff_from_SQ_bag = dplyr::case_when(Value_bag == 0 ~"NA", TRUE ~ Diff_from_SQ_bag), 
                Diff_from_SQ_size = dplyr::case_when(Value_bag == 0 ~"NA", TRUE ~ Diff_from_SQ_size),
                Diff_from_SQ_Season = dplyr::case_when(Value_bag == 0 ~"NA", TRUE ~ Diff_from_SQ_Season),
                Value_bag = dplyr::case_when(Value_bag == 0 ~"NA", TRUE ~ Value_bag)) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(Diff_from_SQ = paste0(Diff_from_SQ_bag,Diff_from_SQ_size,Diff_from_SQ_Season)) %>% 
  dplyr::select(!c(Diff_from_SQ_bag,Diff_from_SQ_size,Diff_from_SQ_Season)) %>% 
  
  #dplyr::filter(!Value_bag == 0) %>%
  #dplyr::group_by(mode, run_number) %>% 
  tidyr::pivot_wider(names_from = Species, values_from = c(Diff_from_SQ, Value_bag, Value_size, Value_Season)) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(cod_bag = paste0(Value_bag_Cod1, " , ", Value_bag_Cod2), 
                cod_size = paste0(Value_size_Cod1, " , ", Value_size_Cod2),
                cod_season = paste0(Value_Season_Cod1, " , ", Value_Season_Cod2),
                had_bag = paste0(Value_bag_Had1, " , ", Value_bag_Had2, " , ", Value_bag_Had3),
                had_size = paste0(Value_size_Had1, " , ", Value_size_Had2, " , ", Value_size_Had3),
                had_season = paste0(Value_Season_Had1, " , ", Value_Season_Had2, " , ", Value_Season_Had3),
                cod_bag = stringr::str_remove(cod_bag, " , NA"), 
                cod_size = stringr::str_remove(cod_size, " , NA"),
                cod_season = stringr::str_remove(cod_season, " , NA"),
                had_bag = stringr::str_remove(had_bag, " , NA"),
                had_size = stringr::str_remove(had_size, " , NA"),
                had_season = stringr::str_remove(had_season, " , NA"), 
                cod_bag = stringr::str_remove(cod_bag, "NA ,"), 
                cod_size = stringr::str_remove(cod_size, "NA ,"),
                cod_season = stringr::str_remove(cod_season, "NA ,"),
                had_bag = stringr::str_remove(had_bag, "NA ,"),
                had_size = stringr::str_remove(had_size, "NA ,"),
                had_season = stringr::str_remove(had_season, "NA ,"),
                Diff_from_SQ_cod = paste0(Diff_from_SQ_Cod1, " , ", Diff_from_SQ_Cod2), 
                Diff_from_SQ_had = paste0(Diff_from_SQ_Had1, " , ", Diff_from_SQ_Had2, " , ", Diff_from_SQ_Had3), 
                Diff_from_SQ_cod = stringr::str_remove(Diff_from_SQ_cod, " , NA"),
                Diff_from_SQ_cod = stringr::str_remove(Diff_from_SQ_cod, "NANA"),
                
                Diff_from_SQ_cod = stringr::str_remove(Diff_from_SQ_cod, "NA ,"),
                Diff_from_SQ_had = stringr::str_remove(Diff_from_SQ_had, "NA ,"),
                Diff_from_SQ_had = stringr::str_remove(Diff_from_SQ_had, " , NA"), 
                Diff_from_SQ_had = stringr::str_remove(Diff_from_SQ_had, " , NANA"), 
                Diff_from_SQ_had = stringr::str_remove(Diff_from_SQ_had, "NANA")) %>% 
  dplyr::select(mode, run_number, Diff_from_SQ_cod, Diff_from_SQ_had, cod_bag, cod_size, cod_season, had_bag, had_size, had_season) %>% 

  
  # dplyr::rename(Mode = mode,
  #               `Bag Limit` = Value_bag,
  #               `Min Size (in)` = Value_size, 
  #               Season = Value_Season) %>%
  # tidyr::separate(Species, into = c("Species"), sep = "(?<=[A-Za-z])") %>%
  # dplyr::mutate(Species = dplyr::recode(Species, "C" = "Cod", "H" = "Haddock"),
  #               Mode = dplyr::recode(Mode, "FH" = "For Hire", "PR" = "Private")) %>%
  # 
  # tidyr::separate(Season, into = c("Season1", "Season2"), sep = " - ") %>% 
  dplyr::mutate(cod_season = stringr::str_remove(cod_season, "2024-"), 
                cod_season = stringr::str_remove(cod_season, "2025-"), 
                had_season = stringr::str_remove(had_season, "2024-"), 
                had_season = stringr::str_remove(had_season, "2025-"), 
                cod_season = stringr::str_remove(cod_season, "2024-"), 
                cod_season = stringr::str_remove(cod_season, "2025-"), 
                had_season = stringr::str_remove(had_season, "2024-"), 
                had_season = stringr::str_remove(had_season, "2025-"), 
                cod_season = stringr::str_remove(cod_season, "2024-"), 
                cod_season = stringr::str_remove(cod_season, "2025-"), 
                had_season = stringr::str_remove(had_season, "2024-"), 
                had_season = stringr::str_remove(had_season, "2025-"), 
                cod_season = stringr::str_remove(cod_season, "2024-"), 
                cod_season = stringr::str_remove(cod_season, "2025-"), 
                had_season = stringr::str_remove(had_season, "2024-"), 
                had_season = stringr::str_remove(had_season, "2025-")) #%>% 
  #  dplyr::select(run_number, Species, Mode, `Bag Limit`, `Min Size (in)`, Season, Diff_from_SQ) %>% 
  # dplyr::group_by(run_number, Mode) %>% 
  # tidyr::pivot_wider(names_from = Species, values_from = c(`Bag Limit`, `Min Size (in)`, Season, Diff_from_SQ), )
  

DT::datatable(Regs_out)
```





# Recreational Cod and and Haddock Mortality

This figure plots the predicted Cod and Haddock recreational mortality for previously simulated management measures.  

Cod: 

* The Cod ACL is the dashed line.  
* Cod mortality is plotted on the **horizontal** axis.
* Regulations with average mortality under the cod ACL are to the **left** of the dashed vertical line. 

Haddock:

* The Haddock ACL is the solid line.  
* Haddock mortality is plotted on the **vertical** axis.
* Regulations with average mortality under the Haddock ACL are **below** the solid line. 

```{r ,  echo  = FALSE, warning = FALSE, message = FALSE}

 catch_agg<- df2 %>%
      #predictions_out %>%
      dplyr::filter(catch_disposition %in% c("keep", "Discmortality"),
                    number_weight == "Weight") %>%
   
      dplyr::group_by(run_number, Category) %>%
      dplyr::summarise(Value = sum(as.numeric(Value))) %>%
   dplyr::mutate(Value = Value * lb_to_mt) %>%
      dplyr::mutate(under_acl = dplyr::case_when(Category == "cod" & Value <= cod_acl ~ 1, TRUE ~ 0),
                    under_acl = dplyr::case_when(Category == "had" & Value <= had_acl ~ 1, TRUE ~ under_acl)) %>%
      dplyr::group_by(run_number, Category) %>%
      dplyr::summarise(under_acl = sum(under_acl),
                       Value = median(Value)) %>% 
   tidyr::pivot_wider(names_from = Category, values_from = c(Value, under_acl)) 

test<- 1:5
p<- catch_agg %>% 
  dplyr::mutate(under_acl_cod = as.integer(under_acl_cod)) %>% 
  ggplot2::ggplot(aes(x = Value_cod, y = Value_had))+
  geom_point(aes(label = run_number, colour = test)) +
  scale_colour_gradient2(low = "white", high = "darkgreen") +
   #geom_text(aes(label = run_number, y = Value_had + 0.25))+
   geom_text(aes(label=run_number))+
   #geom_text(aes(label=ifelse(Value_cod>cod_acl & Value_had > had_acl, as.character(run_number), ' '), hjust=1, vjust=1))+
   geom_vline( xintercept =cod_acl, linetype="dashed")+
   geom_hline( yintercept =had_acl, color="grey45")+
   scale_colour_gradient(low = "white", high = "darkgreen")+
   ggtitle("Cod and Haddock Mortality")+
   ylab("Total Haddock Mortality (mt)")+
   xlab("Total Cod Mortality (mt)")

fig<- plotly::ggplotly(p, 
                       tooltip = c("x", "y", "colour")) %>% 
  plotly::style(textposition = "top")

fig
#gridExtra::grid.arrange(fig1, fig2, ncol = 2)

```

## Plots {.tabset}

###  Mortality and CV

```{r ,  echo  = FALSE, warning = FALSE, message = FALSE}

  welfare <-  df2 %>%
          dplyr::filter(Category %in% c("CV")) %>%
          dplyr::group_by(run_number, option, Category, draw_out) %>%
          dplyr::summarise(Value = sum(as.numeric(Value))) %>%
          dplyr::group_by(run_number,option, Category) %>%
          dplyr::summarise(CV = median(Value))


        catch<- df2 %>%
          dplyr::filter(catch_disposition %in% c("keep", "Discmortality"),
                        number_weight == "Weight") %>%
          dplyr::group_by(run_number, option, Category, draw_out) %>%
          dplyr::summarise(Value = sum(as.numeric(Value))) %>%
          dplyr::mutate(Value = Value * 0.000454) %>%
          dplyr::group_by(run_number, option, Category) %>%
          dplyr::summarise(Value = median(Value)) %>%
          tidyr::pivot_wider(names_from = Category, values_from = Value) %>%
          dplyr::left_join(welfare) %>%
          dplyr::select(!Category)
        
        p1<- catch %>% ggplot2::ggplot(aes(x = cod, y = CV))+
          geom_point() +
          geom_vline( xintercept =cod_acl)+
          geom_text(aes(label=run_number, hjust=1, vjust=1))+
          ggtitle("Cod - Consumer Surplus")+
          ylab("Consumer Surplus ($)")+
          xlab("Total Cod Mortality")+
          theme(legend.position = "none")

        fig1<- ggplotly(p1) %>% 
          plotly::style(textposition = "top")

        fig1

        p2<- catch %>% ggplot2::ggplot(aes(x = had, y = CV))+
          geom_point() +
          geom_vline( xintercept =had_acl)+
          geom_text(aes(label=run_number, hjust=1, vjust=1))+
          ggtitle("Haddock - Consumer Surplus")+
          ylab("Consumer Surplus ($)")+
          xlab("Total Haddock Mortality")+
          theme(legend.position = "none")

        fig2<- ggplotly(p2) %>% 
          plotly::style(textposition = "top")

        fig2

```


###  Mortality and Releases

```{r ,  echo  = FALSE, warning = FALSE, message = FALSE}

 release <-  df2 %>%
          dplyr::filter(catch_disposition %in% c("release")) %>%
          dplyr::group_by(run_number, option, Category, draw_out) %>%
          dplyr::summarise(Value = sum(as.numeric(Value))) %>%
          dplyr::group_by(run_number,option, Category) %>%
          dplyr::summarise(release = median(Value))


        catch<- df2 %>%
          dplyr::filter(catch_disposition %in% c("keep", "Discmortality"),
                        number_weight == "Weight") %>%
          dplyr::group_by(run_number, option, Category, draw_out) %>%
          dplyr::summarise(Value = sum(as.numeric(Value))) %>%
          dplyr::mutate(Value = Value * lb_to_mt) %>%
          dplyr::group_by(run_number, option, Category) %>%
          dplyr::summarise(Value = median(Value)) %>%
          dplyr::left_join(release) %>%
          tidyr::pivot_wider(names_from = Category, values_from = c(Value, release))
        
        
         p3<- catch %>% ggplot2::ggplot(aes(x = Value_cod, y = release_cod))+
          geom_point() +
          geom_vline( xintercept = cod_acl)+
          geom_text(aes(label=run_number), nudge_x = 0.25, nudge_y = 0.25, check_overlap = T)+
          ggtitle("Cod Releases")+
          ylab("Released Cod")+
          xlab("Total Cod Mortality (mt)")+
          theme(legend.position = "none")

        fig3<- ggplotly(p3)%>%
          plotly::style(textposition = "top")
        fig3
        

        p4<- catch %>% ggplot2::ggplot(aes(x = Value_had, y = release_had))+
          geom_point() +
          geom_vline( xintercept = had_acl)+
          geom_text(aes(label=run_number), nudge_x = 0.25, nudge_y = 0.25, check_overlap = T)+
          ggtitle("Haddock Releases")+
          ylab("Released Haddock")+
          xlab("Total Haddock Mortality (mt)")+
          theme(legend.position = "none")

        fig4<- ggplotly(p4)%>%
          plotly::style(textposition = "top")
        fig4

```

### Trips

```{r,  echo  = FALSE, warning = FALSE, message = FALSE}

     trips <-  df2 %>%
  dplyr::filter(Category %in% c("ntrips")) %>%
  dplyr::group_by(run_number, option, Category, draw_out) %>%
  dplyr::summarise(Value = sum(as.numeric(Value))) %>%
  dplyr::group_by(run_number,option, Category) %>%
  dplyr::summarise(trips = median(Value)) 
  
  
catch<- df2 %>% 
  dplyr::filter(catch_disposition %in% c("keep", "Discmortality"),
                number_weight == "Weight") %>%
  dplyr::group_by(run_number, option, Category, draw_out) %>%
  dplyr::summarise(Value = sum(as.numeric(Value))) %>%
  dplyr::mutate(Value = Value * lb_to_mt) %>%
  dplyr::group_by(run_number, option, Category) %>%
  dplyr::summarise(Value = median(Value)) %>% 
  tidyr::pivot_wider(names_from = Category, values_from = Value) %>% 
  dplyr::left_join(trips) %>% 
  dplyr::select(!Category) 

 p5<- catch %>% ggplot2::ggplot(aes(x = cod, y = trips))+
   geom_point() +
   #geom_vline( xintercept =cod_acl)+
  geom_text(aes(label=run_number, hjust=1, vjust=1))+
   ylab("Total Number of Trips")+
   xlab("Recreational Cod Mortality (mt)")+
   theme(legend.position = "none")
 
fig5<- ggplotly(p5)%>% 
  plotly::style(textposition = "top")

fig5


 p6<- catch %>% ggplot2::ggplot(aes(x = had, y = trips))+
   geom_point() +
   #geom_vline( xintercept =cod_acl)+
  geom_text(aes(label=run_number, hjust=1, vjust=1))+
   ylab("Total Number of Trips")+
   xlab("Recreational Haddock Mortality (mt)")+
   theme(legend.position = "none")
 
fig6<- ggplotly(p6)%>% 
  plotly::style(textposition = "top")

fig6


```

