---
title: "Cod and Haddock Model Summary <br> `r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

This page summarizes models results for sets of policies that have been run to date.  These are intended as a jumping off point for your own model runs.  


The results of your own model runs are stored. Please give it a name (please no underscores "_" ).  At the end of the day, they are added to this page.  

Hover over each point to view the detailed statistics for each model run.  The first section contains a table of recreational management measures. The second section contains graphs of mortality.   The third section has graphs of other performance measures, including Economic Surplus, Trips, and Discards. 

```{r setup, echo  = FALSE, warning = FALSE, message = FALSE}

library(tidyverse)
library(grid)
library(plotly)
df <- list.files(path=here::here("output/"),pattern = "*.csv",full.names = T) %>% 
  map_df(~data.table::fread(.,stringsAsFactors=F,check.names=T,strip.white=T))

test<- read.csv(here::here("output/output_20241120_145146.csv"))

df2<- df %>% dplyr::mutate(run_number = as.character(rep(1:(length(df$mode)/90), each = 90)))

cod_acl <- 99
had_acl <- 1075
lb_to_mt <-  0.000454
```

# Management Measures

```{r,  echo  = FALSE, warning = FALSE, message = FALSE}
SQ_regulations <- read.csv(here::here("data-raw/SQ_regulations.csv")) %>% 
  dplyr::rename(Category = Var, 
                SQ = Val)
df3<- df2 %>% dplyr::filter(!Category %in% c("CV", "ntrips", "nchoiceoccasions","cod" , "had")) %>% 
  dplyr::select(Category, Value, run_number) %>% 
  dplyr::left_join(SQ_regulations, by = c("Category")) 

seas<- df3 %>% dplyr::filter(stringr::str_detect(Category, "Season")) %>% 
  tidyr::separate(Value, into = c("Value1", "Value2"), sep = " - ") %>% 
  tidyr::separate(SQ, into = c("SQ1", "SQ2"), sep = " - ") %>% 
  dplyr::mutate(Value = as.integer(lubridate::ymd(Value2)-lubridate::ymd(Value1)), 
                SQ = as.integer(lubridate::ymd(SQ2)-lubridate::ymd(SQ1))) %>% 
  dplyr::mutate(Diff_from_SQ = dplyr::case_when(Value < SQ ~ "Shorter_Season", TRUE ~ ""),
                Diff_from_SQ = dplyr::case_when(Value > SQ ~ "Longer_Season", TRUE ~ Diff_from_SQ), 
                Value = paste0(Value1, " - ", Value2)) %>% 
  dplyr::select(Category, Diff_from_SQ, run_number)
                  
bag<- df3 %>% dplyr::filter(stringr::str_detect(Category, "bag")) %>% 
  dplyr::mutate(Diff_from_SQ = dplyr::case_when(as.numeric(Value) < as.numeric(SQ) ~ "Smaller Bag", TRUE ~ ""),
                Diff_from_SQ = dplyr::case_when(as.numeric(Value) > as.numeric(SQ) ~ "Larger Bag", TRUE ~ Diff_from_SQ)) %>% 
  dplyr::select(Category, Diff_from_SQ, run_number)

size<- df3 %>% dplyr::filter(stringr::str_detect(Category, "size")) %>% 
  dplyr::mutate(Diff_from_SQ = dplyr::case_when(as.numeric(Value) < as.numeric(SQ) ~ "Smaller Min Length", TRUE ~ ""),
                Diff_from_SQ = dplyr::case_when(as.numeric(Value) > as.numeric(SQ) ~ "Larger Min Length", TRUE ~ Diff_from_SQ)) %>% 
  dplyr::select(Category, Diff_from_SQ, run_number)

df4<- rbind(seas, bag, size)


Regs_out <- df3 %>%
  dplyr::left_join(df4, by = c("Category", "run_number")) %>% 
  dplyr::select(!SQ) %>% 
  dplyr::select(!Opt) %>% 
  tidyr::separate(Category, into =c("Species", "mode", "Var"), sep = "_") %>%
  dplyr::ungroup() %>% 
  tidyr::pivot_wider(names_from = Var, values_from = c(Value, Diff_from_SQ)) %>%
  dplyr::filter(!Value_bag == 0) %>%
  dplyr::rename(Mode = mode,
                `Bag Limit` = Value_bag,
                `Min Size (in)` = Value_size, 
                Season = Value_Season) %>%
  tidyr::separate(Species, into = c("Species"), sep = "(?<=[A-Za-z])") %>%
  dplyr::mutate(Species = dplyr::recode(Species, "C" = "Cod", "H" = "Haddock"),
                Mode = dplyr::recode(Mode, "FH" = "For Hire", "PR" = "Private")) %>%
  dplyr::mutate('Diff From SQ' = paste0(Diff_from_SQ_bag,Diff_from_SQ_size,Diff_from_SQ_Season)) %>% 
   dplyr::select(run_number, Species, Mode, `Bag Limit`, `Min Size (in)`, Season, 'Diff From SQ')
 DT::datatable(Regs_out)
```





# Recreational Cod and and Haddock Mortality

This figure plots the predicted Cod and Haddock recreational mortality for previously simulated management measures.  

Cod: 

* The Cod ACL is the dashed line.  
* Cod mortality is plotted on the **horizontal** axis.
* Regulations with average mortality under the cod ACL are to the **left** of the dashed vertical line. 

Haddock:

* The Haddock ACL is the solid line.  
* Haddock mortality is plotted on the **vertical** axis.
* Regulations with average mortality under the Haddock ACL are **below** the solid line. 

```{r ,  echo  = FALSE, warning = FALSE, message = FALSE}

 catch_agg<- df2 %>%
      #predictions_out %>%
      dplyr::filter(catch_disposition %in% c("keep", "Discmortality"),
                    number_weight == "Weight") %>%
   
      dplyr::group_by(run_number, Category) %>%
      dplyr::summarise(Value = sum(as.numeric(Value))) %>%
   dplyr::mutate(Value = Value * lb_to_mt) %>%
      dplyr::mutate(under_acl = dplyr::case_when(Category == "cod" & Value <= cod_acl ~ 1, TRUE ~ 0),
                    under_acl = dplyr::case_when(Category == "had" & Value <= had_acl ~ 1, TRUE ~ under_acl)) %>%
      dplyr::group_by(run_number, Category) %>%
      dplyr::summarise(under_acl = sum(under_acl),
                       Value = median(Value)) %>% 
   tidyr::pivot_wider(names_from = Category, values_from = c(Value, under_acl)) %>% 
   dplyr::mutate(run_number = as.numeric(run_number))

p<- catch_agg  %>% 
  ggplot2::ggplot(aes(x = Value_cod, y = Value_had))+
   geom_point(aes(label = run_number, colour = under_acl_cod)) +
   #geom_text(aes(label = run_number, y = Value_had + 0.25))+
   geom_text(aes(label=run_number, hjust=1, vjust=1))+
   #geom_text(aes(label=ifelse(Value_cod>cod_acl & Value_had > had_acl, as.character(run_number), ' '), hjust=1, vjust=1))+
   geom_vline( xintercept =cod_acl, linetype="dashed")+
   geom_hline( yintercept =had_acl, color="grey45")+
   scale_colour_gradient(low = "white", high = "darkgreen")+
   ggtitle("Cod and Haddock Mortality")+
   ylab("Recreational Haddock Mortality (mt)")+
   xlab("Recreational Cod Mortality (mt)")



 
fig<- ggplotly(p)

fig
#gridExtra::grid.arrange(fig1, fig2, ncol = 2)

```

## Plots {.tabset}

###  Mortality and CV

```{r ,  echo  = FALSE, warning = FALSE, message = FALSE}

welfare <-  df2 %>%
  dplyr::filter(Category %in% c("CV")) %>%
  dplyr::group_by(run_number, option, Category, draw_out) %>%
  dplyr::summarise(Value = sum(as.numeric(Value))) %>%
  dplyr::group_by(run_number,option, Category) %>%
  dplyr::summarise(CV = median(Value)) 
  
  
catch<- df2 %>% 
  dplyr::filter(catch_disposition %in% c("keep", "Discmortality"),
                number_weight == "Weight") %>%
  dplyr::group_by(run_number, option, Category, draw_out) %>%
  dplyr::summarise(Value = sum(as.numeric(Value))) %>%
  dplyr::mutate(Value = Value * lb_to_mt) %>%
  dplyr::group_by(run_number, option, Category) %>%
  dplyr::summarise(Value = median(Value)) %>% 
  tidyr::pivot_wider(names_from = Category, values_from = Value) %>% 
  dplyr::left_join(welfare) %>% 
  dplyr::select(!Category) %>% 
  dplyr::mutate(run_number = as.numeric(run_number))

 p1<- catch %>% ggplot2::ggplot(aes(x = cod, y = CV))+
   geom_point() +
   geom_vline( xintercept =cod_acl)+
     geom_text(aes(label=run_number, hjust=1, vjust=1))+
   ggtitle("Cod")+
   ylab("Consumer Surplus ($)")+
   xlab("Recreational Cod Mortality (mt)")+
   theme(legend.position = "none")

 p2<- catch %>% ggplot2::ggplot(aes(x = had, y = CV))+
   geom_point() +
   geom_vline( xintercept =had_acl)+
     geom_text(aes(label=run_number, hjust=1, vjust=1))+
   ggtitle("Hadock")+
   ylab("Consumer Surplus ($)")+
   xlab("Recreational Haddock Mortality (mt)")+
   theme(legend.position = "none")

 
fig1<- ggplotly(p1)
fig2<- ggplotly(p2)
fig1
fig2
#gridExtra::grid.arrange(fig1, fig2, ncol = 2)

```


###  Mortality and Releases

```{r ,  echo  = FALSE, warning = FALSE, message = FALSE}

release <-  df2 %>%
  dplyr::filter(catch_disposition %in% c("release")) %>%
  dplyr::group_by(run_number, option, Category, draw_out) %>%
  dplyr::summarise(Value = sum(as.numeric(Value))) %>%
  dplyr::group_by(run_number,option, Category) %>%
  dplyr::summarise(release = median(Value)) 
  
  
catch<- df2 %>% 
  dplyr::filter(catch_disposition %in% c("keep", "Discmortality"),
                number_weight == "Weight") %>%
  dplyr::group_by(run_number, option, Category, draw_out) %>%
  dplyr::summarise(Value = sum(as.numeric(Value))) %>%
  dplyr::mutate(Value = Value * lb_to_mt) %>%
  dplyr::group_by(run_number, option, Category) %>%
  dplyr::summarise(Value = median(Value)) %>% 
  dplyr::left_join(release) %>%
  tidyr::pivot_wider(names_from = Category, values_from = c(Value, release))

 p1<- catch %>% ggplot2::ggplot(aes(x = Value_cod, y = release_cod))+
   geom_point() +
   geom_vline( xintercept = cod_acl)+
   geom_text(aes(label=run_number, hjust=0, nudge_x=5))+
   ggtitle("Cod")+
   ylab("Consumer Surplus ($)")+
   xlab("Total Cod Mortality")+
   theme(legend.position = "none")

 p2<- catch %>% ggplot2::ggplot(aes(x = Value_had, y = release_had))+
   geom_point() +
   geom_vline( xintercept =had_acl)+
   geom_text(aes(label=run_number, hjust=0, nudge_x=50))+
   ggtitle("Hadock")+
   ylab("Consumer Surplus ($)")+
   xlab("Total Haddock Mortality")+
   theme(legend.position = "none")

 
fig1<- ggplotly(p1)
fig2<- ggplotly(p2)
fig1
fig2
#gridExtra::grid.arrange(fig1, fig2, ncol = 2)

```



```{r}
mtcars %>%
  ggplot2::ggplot(aes(x = mpg, y = disp))+
  geom_point(aes(colour = wt))

```





